### 2022-08-20 manuscript.Rmd
Add code for control models

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = TRUE,
  mixed_models = TRUE
)

@@

# Do the actual preprocessing if requested
if (run$eeg_processing) {

@@

```{r, mixed_models, eval=run$mixed_models}
# Filter relevant conditions for the main analysis
trials %>%
  mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
  drop_na() -> trials_main

@@

# Fit linear mixed models
deps <- c("P1", "N170", "N400")
map(deps, function(dep, model_formula = form, model_data = trials_main) {

  # Modify the formula such that fixed effects are always retained
  model_formula %<>%
    tabulate.formula() %>%
    mutate(block = replace(block, is.na(grouping), "fixed"))

@@

  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
  build <- buildmer(
    buildmerControl = buildmerControl(
      formula = model_formula,
      data = model_data,
      args = list("control" = lme4::lmerControl(
        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
      )),
      direction = c("backward", "backward"),
      cl = cl,
      elim = LRTalpha(.20),
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  stopCluster(cl)

@@

  # Create list of returns
  list(
    "model" = build@model,
    "summary" = build@summary,
    "anova" = build@anova,
    "means" = means,
    "contrasts" = contrasts
  ) %>%
    return()
}) %>%
  # Add ERP component names
  set_names(deps) -> models

# Save models
saveRDS(models, here(output_dir, "models.RDS"))
```

```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
# Read fitted models
models <- readRDS(here(output_dir, "models.RDS"))

# Extract relevant statistics to print in the main text
map(models, function(model) as_tibble(model$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table
map(models, function(model) as_tibble(model$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table

# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

@@

>>>>

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = TRUE,
  mixed_models = TRUE,
  control_analysis = TRUE,
)

@@

# (Re-)do the actual preprocessing if requested
if (run$eeg_processing) {

@@

```{r, mixed_models}
# (Re-)do the actual model fitting if requested
if (run$mixed_models) {

  # Filter relevant conditions for the main analysis
  trials %>%
    mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
    drop_na() -> trials_main

@@

  # Helper function for fitting linear mixed models and computing contrasts
  fit_mixed_models <- function(dep, formula, data) {

    # Modify the formula such that fixed effects are always retained
    formula %<>%
      tabulate.formula() %>%
      mutate(block = replace(block, is.na(grouping), "fixed"))

@@

    # Find the best fitting model (see Matuschek et al., 2017, *JML*)
    build <- buildmer(
      buildmerControl = buildmerControl(
        formula, data,
        args = list("control" = lme4::lmerControl(
          optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
        )),
        direction = c("backward", "backward"),
        cl = cl,
        elim = LRTalpha(.20),
        calc.anova = TRUE,
        ddf = "Satterthwaite",
        dep = dep
      )
    )
    stopCluster(cl)

@@

    # Create list of returns
    list(
      "model" = build@model,
      "summary" = build@summary,
      "anova" = build@anova,
      "means" = means,
      "contrasts" = contrasts
    )
  }

  # Actually fit the model for each component
  deps <- config$components$name
  map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
    set_names(deps) -> models

  # Save models
  saveRDS(models, here(output_dir, "models.RDS"))
} else {

  # Read fitted models
  models <- readRDS(here(output_dir, "models.RDS"))
}

# Extract relevant statistics to print in the main text
map(models, function(model) as_tibble(model$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table
map(models, function(model) as_tibble(model$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table
```

```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

@@

## Control Analysis

```{r, control_analysis}
# (Re-)do the actual model fitting if requested
if (run$mixed_models_control) {

  # Filter relevant conditions for the main analysis
  conditions_control <- c("Informed", "Exclude_informed")
  trials %>%
    mutate(condition = factor(condition, levels = conditions_control)) %>%
    drop_na() -> trials_control

  # Contrast coding for phase
  cbind(
    c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
    c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
  ) %>%
    t() %>%
    ginv() -> contrasts(trials_control$phase)

  # Contrast coding for condition
  cbind(c("Informed" = 1, "Exclude_informed" = -1)) %>%
    t() %>%
    ginv() -> contrasts(trials_control$condition)

  # Fit the model for each component
  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
    set_names(deps) -> models_control

  # Save models
  saveRDS(models_control, here(output_dir, "models_control.RDS"))
} else {

  # Read fitted models
  models_control <- readRDS(here(output_dir, "models_control.RDS"))
}

# Extract relevant statistics to print in the main text
map(models_control, function(mod) as_tibble(mod$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table_control
map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
```
